### 2014-03-14 etc/abstract.tex
update
Alex edits

% 1.Statetheproblem
Mutation analysis is a metric for measuring the quality of test suites. However, it is computationally intensive compared to other measures which it hard to use in practice. Choosing a smaller subset of mutations to run is a simple approach that can alleviate this problem. There exist multiple ways to reduce the set of mutations to run. Operator selection has recently been in the focus. However recently researchers have found that sampling can achive accuracy and mutant reduction similar to operator selection.

%2.Saywhyit’saninterestingproblem
However, which sampling technique is best, is an open problem, especially for real-world programs and test-suites.

%3.Saywhatyoursolutionachieves
Our research compares a number of sampling criteria, and operator selection criteria based on their ability to approximate the full mutation score, and also the consistency of results.

%4.Saywhatfollowsfromyoursolution
Our experiments rank sampling criterias that can be used by testers according how much mutant reduction is achieved, their ability to predict the final mutation score, the relative effect of unit increase in sampled mutation score on the final score, and also the time required for the run. We also find that sampling techniques work better than operator selection methods including statement deletion in both mutation reduction and accuracy of approximation to the full mutation score.

>>>>

% 1.Statetheproblem
Mutation analysis is a well-known method for measuring the quality of
test suites. However, it is computationally intensive compared to
other measures, which makes it hard to use in practice. Choosing a
smaller subset of mutations to run is a simple approach that can
alleviate this problem.  Mutation operator selection has been heavily
researched. Recently, researchers have found that sampling mutants can
achieve accuracy and mutant reduction similar to operator selection.

%2.Saywhyit’saninterestingproblem
However, the statistical support for these conclusions has been limited, due to the small number of subject programs investigated.  The best sampling technique is also an open problem.
% that can be drawn from the previous
%research has been limited due to the small number of subject programs. Further,
%which sampling technique is best is still an open problem that needs to be
%tackled on a much larger range of test subjects.

%3.Saywhatyoursolutionachieves

Our research compares a large number of sampling and operator
selection criteria based on their ability to predict the full mutation
score as well as the consistency of mutation reduction ratios
achieved. Our results provide a ranking that can be used to choose an
appropriate mutation reduction technique by the reduction and level of fidelity to full mutation results required.

%according to the mutation reduction ratio desired, and
%how much reduction in accuracy is acceptable.

%4.Saywhatfollowsfromyoursolution

We find that all sampling approaches perform better than operator
selection methods, when considering ability to predict the full
mutation score as well as the consistency of mutation reduction ratios
achieved.

%and also the consistency of mutation reduction ratios achieved.  Specifically,
%we find that random selection of a mutant performs better than statement
%deletion operator selection criteria.

### 2014-03-14 src/introduction.Rnw
update
Alex edits

% 1. Describe the problem
% 2. State your contributions
Mutation analysis is a method of evaluating the quality of test-suites. It
involves producing a family of mutants with simple differences from the
original program, and evaluating the effectiveness of test-suites against
these mutants~\cite{lipton1971fault, ammann2008introduction}.  Previous
research~\cite{andrews2005mutation} suggests that mutations thus introduced
behave in a fashion similar to the real-faults with respect to the difficulty
of detection.

One of the impediments to wider adoption of mutation analysis is its high
computational cost.  The set of simple mutants of a moderate sized program
can be very large, and renders mutation analysis prohibitively time-consuming.

A major strain of research into cost-reduction of mutation
analysis is to choose a smaller representative set of
mutants~\cite{offutt2001mutation,jia2011analysis}-- often called the \textit{do
fewer} approach. This approach can be generally divided into selective
strategies and sampling strategies.

Selective mutation strategies attempt to select a representative subset of
operators based on heuristics and statistical analysis, and applying this
subset of operators to generate mutants instead of applying the whole gamut
of mutation operators~\cite{offutt1993anexperimental,untch2009onreduced}.

Sampling strategies seek to randomly select smaller representative
mutants.  This was investigated first by Acree~\cite{acree1980mutation} and
Budd~\cite{budd1980mutation}, who proposed using only $x$\% of the mutants
produced. The studies by Wong and Mathur found that random sampling with
ratio as low as 10\% could provide accurate results~\cite{jia2011analysis}.

@@

A few recent works~\cite{zhang2010icse,zhang2013ase} have investigated the
relative merits of random sampling strategies and operator selection. It
was found that while random sampling can generally perform equal to or
better than operator selection, a strategy that combined random sampling
with program elements paid superior dividends.

However, as pointed out by Zhang et al.~\cite{zhang2013ase}, the
field has a serious lacuna in large scale research, both in the
size of the programs studied, and in the number and diversity of
programs, which reduces our confidence in their results. This is
true for selective mutation studies, studies in sampling, and also
for comparatively newer studies that attempt to combine them. This
is particularly worrisome if mutation analysis is to gain wider
acceptance among testing professionals. Further, quite a few of the influential
studies~\cite{offutt1993experimental,offutt1996anexperimental,wong1995reducing,mresa1999efficiency}
has been conducted on older programming languages such as Fortran with
operators specific to it, and are not directly applicable to newer
languages such as Java, with significant differences. Finally, with the
modern research into the byte code based mutation (a \textit{do smarter}
approach for eliminating the compilation step, and gaining execution speed)
operators based on source code modification is no longer be applicable,
and their equivalents in the bytecode needs to be found and compared with
other approaches. A detailed discussion of these issues can be found in
Section~\ref{sec:related}.

We have attempted to rectify this situation with a large scale study of
industrial programs.  As detailed in Section~\ref{sec:methodology}, we sample
188 real world Java programs from Github, with size ranging from 50loc to
100kloc, which allows widely applicable statistical inferences to be made. We
provide the results from running both original human generated test-suites, and
also programmatically generated test-suites, increasing the applicability of
our findings to both researchers who seek to compare test-suites quickly,
and to industrial software testers who might be looking for a way to
reduce the time of their build cycle when using mutation coverage. The
Section~\ref{sec:methodology} discusses the sampling strategies attempted,
and the operator selection strategies in detail, and the results of our
experiment are given in Section~\ref{sec:results}, followed by detailed
discussion of what it implies in section ~\ref{sec:discussion}. The research
concludes in Section~\ref{sec:conclusion}.

Our specific contributions in this paper are listed as follows:

@@

\item Our study is the largest so far in terms of both the size of programs
involved (50loc to 100kloc), and the number of programs analyzed (188
unique open source projects) for mutant reduction strategies. This allows
for stronger and widely applicable statistical inferences to be drawn.

\item We compare a much large number of mutant reduction strategies,
especially with respect to their predictive power over the final mutation
score, the expected mutant reduction, and the stability of the amount of
mutant reduction expected. Our sampling strategies include some that were
suggested by other researchers, and also a few novel strategies that has
not been published elsewhere.

\item Our recommendations are valid for both testing researchers who might
be comparing programmatically generated test-suites, and software testing
professionals working on real test-suites.

@@

>>>>

% 1. Describe the problem % 2. State your contributions Mutation
analysis is a method for evaluating the quality of test-suites. It
involves producing a family of \emph{mutants}, programs with small
differences from the original program, and evaluating the
effectiveness of test suites against these
mutants~\cite{lipton1971fault, ammann2008introduction}.  Previous
research~\cite{andrews2005mutation} suggests that mutations thus
introduced behave in a fashion similar to real faults, with respect to
the difficulty of detection.

One of the impediments to wider adoption of mutation analysis is its
high computational cost.  The set of simple mutants for even a
moderate sized program can be very large, which renders mutation
analysis prohibitively time consuming.

A major strain of research into cost-reduction of mutation analysis is
to choose a smaller, representative, set of
mutants~\cite{offutt2001mutation,jia2011analysis} --- often called the
\textit{do fewer} approach. This approach can be generally divided
into selective strategies and sampling strategies.

Selective mutation strategies attempt to select a representative
subset of mutation \emph{operators} based on heuristics and
statistical analysis, and apply this subset of operators to generate
mutants instead of applying the whole set of mutation
operators~\cite{offutt1993anexperimental,untch2009onreduced}.  As an
example, recent work suggests that using statement deletion only can
provide effective mutation analysis~\cite{untch2009onreduced}.

Sampling strategies seek to randomly select a set of representative
mutants.  This was investigated first by
Acree~\cite{acree1980mutation} and Budd~\cite{budd1980mutation}, who
proposed using only $x$\% of all mutants produced. Wong and Mathur
found that random sampling with ratio as low as 10\% could provide
accurate results~\cite{jia2011analysis}.

@@

Recent work~\cite{zhang2010icse,zhang2013ase} has investigated the
relative merits of random sampling strategies and operator selection.
Random sampling can perform as well as or better than operator
selection, in these studies; a strategy combining random sampling with
program element-based sampling was best.  {\bf ADG: did it combing
random with pelem or pelem with operator???}

However, as pointed out by Zhang et al.~\cite{zhang2013ase}, the field
has a serious lacuna in large scale research, both in the size of the
programs studied, and in the number and diversity of programs, which
reduces our confidence in all results. This is true for selective
mutation studies, studies in sampling, and also for comparatively
newer studies that attempt to combine methods. This is particularly
worrisome if mutation analysis is to gain wider acceptance among
testing professionals. Further, quite a few of the influential
studies~\cite{offutt1993experimental,offutt1996anexperimental,wong1995reducing,mresa1999efficiency}
were conducted on older programming languages such as Fortran, with
operators specific to the language, and are not directly applicable to
newer languages such as Java. Finally, modern research into the byte
code based mutation (a \textit{do smarter} approach for eliminating
the compilation step to gain execution speed) operators based on
source code modification are no longer applicable, and their
equivalents in bytecode need to be identified and compared with other
approaches. A detailed discussion of these issues can be found in
Section~\ref{sec:related}.

We have attempted to rectify this situation with a large scale study
of real world programs.  As detailed in Section~\ref{sec:methodology},
we sample 188 Java programs from Github, with size ranging from 50 LOC
to 100 KLOC, which allows widely applicable statistical inferences to
be made. We provide the results from running both original project
human generated test-suites and also automatically generated
test suites using random testing, increasing the applicability of our
findings to both testers in traditional development who are interested in applying mutation analysis to suite evaluation and to researchers who seek to compare test suites quickly.

Section~\ref{sec:methodology} discusses the sampling and operator
selection strategies we study in detail, and the results of our
experiment are given in Section~\ref{sec:results}, followed by
detailed discussion of what these results imply in Section
~\ref{sec:discussion}. The specific contributions of this paper are:

%The research concludes in Section~\ref{sec:conclusion}.

@@

\item Our study is the largest so far in terms of both the size of programs
involved (50 LOC to 100 KLOC), and the number of programs analyzed (188
unique open source projects) for mutant reduction strategies. This allows
for stronger and more widely applicable conclusions about effectiveness.

\item We compare a much large number of mutant reduction strategies
than previous studies. We compare with respect to the predictive power
(correlation) with the full mutation score, expected mutant reduction,
and the stability of the amount of mutant reduction expected. Our
sampling strategies include some that were suggested by other
researchers, as well as a few novel strategies that have not been
previously considered.

\item Our recommendations are valid for both testing researchers who
might be comparing automatically generated test-suites, and software
testers in real world development working to produce and evaluate manual test suites.

@@

Our data is available for replication~\cite{data}\footnote{Available on publication}.
